---
title: "STISIM-Dat-File-Cleaining"
author: "Hayden Green"
date: "18 July 2018"
output: html_document
---

## Data Cleaning File
### Import the Packages 

```{r results='hide', error=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(xlsx)
```

#

```{r results='hide'}

```

### Choose the raw data file to be cleaned

Errors may appear when running this dialog if there is a problem with using your google drive or other file directories are inaccesible to R

```{r}
filename_Database <- "G:\\Team Drives\\Research Team\\Projects\\2018 Driving Sim Reproducibility\\Participant Information.xlsx" 
list_of_DAT_files <- read_xlsx(filename_Database, sheet = "Scenario Coding") %>% 
  mutate(pattern_name = paste0(Participant,"_", Run_Number))
        
list_of_DAT_files %>% head()

  
list.files(path = "G:/Team Drives/Research Team/Projects/2018 Driving Sim Reproducibility/3_Raw Data/", pattern = "?NS_3.Dat", recursive = TRUE, full.names = TRUE)

filename <- list.files(path = "G:/Team Drives/Research Team/Projects/2018 Driving Sim Reproducibility/3_Raw Data/", pattern = list_of_DAT_files$pattern_name[1], recursive = TRUE, full.names = TRUE)
```

### Import the file
The file is imported, the start and end of the numerical raw data file is idenitifed and selected into a data frame called "cleaned_data", it is sorted based on the vector "Sorted_columns" above.

```{r}
clean_DAT <- function (x) {

if(length(list.files(path = "G:/Team Drives/Research Team/Projects/2018 Driving Sim Reproducibility/3_Raw Data/",
                              pattern = paste0("?",x,"_trimmed"), recursive = TRUE, full.names = TRUE)) >= 1) {
    print(paste(x , "is Trimmed"))
  
    } else {
    
  filename <- list.files(path = "G:/Team Drives/Research Team/Projects/2018 Driving Sim Reproducibility/3_Raw Data/", 
                         pattern = paste0("?",x,".Dat"), recursive = TRUE, full.names = TRUE)
  
## Define the column names that are in the DAT files and then sorting them in a more preferred order.

  Columns <- c("Elapsed_Time","Longitudinal_Accel","Lateral_Accel","Longitudinal_Veloc","Lateral_Veloc","Total_dist","Lateral_Lane_Pos","Vehic_curve","Road_Curve","Steering_angle","Throttle_input","Brake_input","Crashes_comp","Marker","Speed","Steering_count","Throttle_count","Brake_Count","System_Time","RT","Trigger_Number","Speed_Limit","Left_indicator","Right_Indicator", "Driving_Tickets")

sorted_columns <- c("Elapsed_Time","Total_dist","Longitudinal_Veloc","Speed","Longitudinal_Accel", "Lateral_Lane_Pos", "Lateral_Veloc", "Lateral_Accel", "Throttle_input", "Brake_input", "Steering_angle","Throttle_count", "Brake_Count", "Steering_count", "Left_indicator", "Right_Indicator","Vehic_curve","Road_Curve", "Speed_Limit","Driving_Tickets", "Trigger_Number", "Crashes_comp", "Marker", "RT","System_Time")
  
  
raw_data <- read.table(filename,sep = "", col.names = Columns, header = FALSE, fill = TRUE,
                        blank.lines.skip = FALSE, stringsAsFactors = FALSE)

data_start <- raw_data[raw_data$Elapsed_Time == "Block",] %>% 
  row.names.data.frame() %>% 
  as.numeric() + 2

data_end <- raw_data[raw_data$Elapsed_Time == "Tailgating",] %>% 
  row.names.data.frame() %>% 
  as.numeric() - 3

cleaned_data <- raw_data[data_start:data_end,sorted_columns]

## Get the summary data of performance and violations. Reads the file into a character string format then select lines starting from the start of the summary data in the file to the end of the file. 

raw_txt <- readLines(filename)
last_line <- length(raw_txt)
summary_report <- raw_txt[grep("Tailgating results",raw_txt):last_line]

summary_report %>% head()

summary_report %>% tail()


Participant_ID <- raw_data[3,2]
Run_number <- raw_data[10,3]

## Obtain the name & path of the data file and create file nimes for the cleaned data
## There is also a function at the bottom which adds additoinal columns for the particpant ## ID and the run number. 

data_filename <- paste(Participant_ID, Run_number, "trimmed", sep = "_")
summary_filename <- paste(Participant_ID, Run_number, "summary", sep = "_")
Pattern <- paste(Participant_ID,"_",Run_number,".Dat", sep = "")
path <- filename %>% str_replace(Pattern, "")
cleaned_data$ID <- Participant_ID %>% rep(nrow(cleaned_data))
cleaned_data$Run_Number <- Run_number %>% rep(nrow(cleaned_data))
cleaned_data$Date <- file.info(filename)$mtime %>% as.Date() %>% rep(nrow(cleaned_data))

## Write the cleaned and summary data into a csv and .txt 
## The raw csv file is "..._cleaned.csv" with the .txt file in "..._summary.txt" file.

cleaned_data %>% write.csv(file = paste(path,data_filename,".csv", sep = ""), row.names = FALSE)
write(summary_report,file = paste(path,summary_filename, ".txt",sep = ""))

print(paste(x, "has now been Trimmed")) }

 
 }

```


```{r}
lapply(list_of_DAT_files$pattern_name, clean_DAT)

```

